Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language

### 2019-01-13 Publication/tex_manuscript/manuscript.tex
tex code formatting

\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
\affil{Publishing / SPi}

@@

\begin{abstract}
This article describes how to use the ``CLV3'' class file, developed by {\sf SPi},
to produce typeset papers based on Computer Linguistics typesetting specifications
for submission to MIT. This document was produced using ``{\tt clv3}'' class file
and will be modified whenever there is an update in the layout specifications.
\end{abstract}

>>>>

\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: rjjarvis@asu.edu.}}
\affil{School of Life Sciences ASU}

@@

\begin{abstract}
This article describes how we scrapped a wide variety of written word from the internet, and then analysed scrapped samples, in order to better charecterize the readability of scientific and non scientific writings.
\end{abstract}
